Trajectory Mapping Results

### 2021-03-24 scripts/analyze_trajectories.Rmd
wip mt

```{r parser, echo = FALSE}
library(tidyverse)
# Parser -----------------------------------------------------------------------
# argsR <- commandArgs(TRUE)
# args_list <- str_split(paste(argsR, collapse=""), pattern="--")
# args_llist <- lapply(args_list, function(x) str_split(x, pattern="="))
# argsDF <- as.data.frame(do.call("rbind", args_llist[[1]]))
# args <- as.list(as.character(argsDF$V2))
# names(args) <- argsDF$V1
# args$burnin <- as.integer(args$burnin)
# args$n <- as.integer(args$n)
# title <- paste("Analysis", gsub("\\.", " ", gsub(".TL.traj", " particles", str_split(args$args, "/")[[1]][3])))
# ---
# subtitle: "`r title`"
# ---
```

@@

```{r debugging}
# Debugging
args = list()
args$burnin = 0.1
args$demes = read.csv("./files/demes_China.csv", stringsAsFactors = FALSE)
args$args = "/Users/maceci/europe10last/210205_europe10.10000.TL.traj"
args$metadata =  "./results/europeC/final_metadata.tsv"
args$n = 10
demes = args$demes
demes$exclude_country[5] = "France,Germany,Italy,Spain"
demes <- demes %>% arrange(deme)
```

## Deme configuration
\tiny
```{r demeconfig}
# Load demes configuration and sequence metadata -------------------------------
# demes <- data.frame(deme = NA, region = NA, country = NA, division = NA,
#                     exclude_country = NA, exclude_division = NA,
#                     min_date = NA, max_date = NA, seq_per_deme = NA) %>%
#   bind_rows(bind_rows(lapply(yaml::yaml.load(string = gsub(",", ", ", gsub(":", ": ", args$demes))),
#                           data.frame, stringsAsFactors = FALSE), .id = "deme")) %>%
#   group_by(deme) %>%
#   mutate(exclude_country = ifelse(is.na(exclude_country), NA, paste0(exclude_country, collapse = ","))) %>%
#   distinct() %>%
#   filter_all(any_vars(!is.na(.))) %>%
#   mutate(deme = str_to_title(deme)) %>%
#   mutate(deme = ifelse(deme %in% c("Othereuropean", "OtherEuropean"), "Other European", deme)) %>%
#   arrange(deme)

@@

## First introductions to each country, source
```{r first-bycountry, fig.height=4}
# 2.2b First introduction into each country, distribution density destination
m = 1
first_country <- df_traj %>%
  mutate(partner = ifelse(var == "O", "China", partner)) %>%
  # 1. Prepare data
  filter(var == "IM" & deme != "China"| var == "O" & deme == "China", !is.na(partner), value != 0) %>%
  group_by(traj, deme) %>%
  arrange(date, partner) %>%
  slice(1:m)

@@

```{r first-times, fig.height=4}
# 2. First introduction distribution density by deme and time of first official reported case to ECDC
first_times <- df_traj_cases %>%
  # 1. Prepare data
  filter(var == "IM" | var == "O", value != 0) %>%
  group_by(deme, traj) %>%
  arrange(date) %>%
  slice(1) %>%
  ungroup %>%
  bind_rows(df_traj_cases %>%
              filter(var == "IM", value != 0) %>%
              group_by(traj) %>%
              arrange(date) %>%
              slice(1)  %>%
              mutate(deme = "Europe")) %>%
  mutate(deme = fct_rev(deme)) %>%
  # 2. Plot
  ggplot() +
  geom_density_ridges(aes(x = date, y = deme, fill = deme), color = "grey50", quantile_lines = TRUE, quantiles = c(0.025, 0.5, 0.975), bandwidth=2, alpha = 0.7, size = 0.2) +
  #stat_density_ridges(, alpha = 0.7)
  #geom_histogram(aes(x = date, fill = deme), bandwidth=5, alpha = 0.7, size = 0.2) +
  #geom_vline(aes(xintercept = min_date, color = dest), linetype = 2) +
  geom_point(data = first_ecdc, 
             aes(date, deme, fill = deme), color = "grey50", shape = 23, size = 3) +
  scale_fill_manual(values = c(dcolors, "Europe" = "grey")) +
  scale_color_manual(values = c(dcolors, "Europe" = "grey")) +
  scale_x_date(limits = c(ymd("2019-10-01"), ymd("2020-03-08")), date_breaks = "1 month", date_labels = "%b %Y", expand = c(0,0)) +
  scale_y_discrete(expand = c(0.05,0), "probability") +
  #theme_ridges() +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        panel.grid.major.x =  element_line(colour = "grey80", size = 0.3, linetype = 2),
        panel.grid.major.y =  element_line(colour = "grey80", size = 0.3, linetype = 1),
        #panel.grid.minor.x =  element_line(colour = "grey80", size = 0.2,  linetype = 3),
        #axis.title.y=element_blank(),
        panel.background = element_rect(fill = "white", colour = "white"))

@@

```{r bvsm-table, results = 'asis'}
for (d in demes$deme) {
  cat("\n## Local transmission vs imported cases - ", d, "\n")
  knitr::kable(hsummary %>% filter(deme == d))
  cat("\n")
}
```

@@

@@

## Weekly incidence population %

>>>>

```{r parser, echo = FALSE}
library(tidyverse)
# Parser -----------------------------------------------------------------------
argsR <- commandArgs(TRUE)
args_list <- str_split(paste(argsR, collapse=""), pattern="--")
args_llist <- lapply(args_list, function(x) str_split(x, pattern="="))
argsDF <- as.data.frame(do.call("rbind", args_llist[[1]]))
args <- as.list(as.character(argsDF$V2))
names(args) <- argsDF$V1
args$burnin <- as.integer(args$burnin)
args$n <- as.integer(args$n)
title <- paste("Analysis", gsub("\\.", " ", gsub(".TL.traj", " particles", str_split(args$args, "/")[[1]][3])))
```

---
subtitle: "`r title`"
---

@@

```{r debugging}
# Debugging
# args = list()
# args$burnin = 0.1
# args$demes = read.csv("./files/demes_China.csv", stringsAsFactors = FALSE)
# args$args = "/Users/maceci/europe10last/210205_europe10.10000.TL.traj"
# args$metadata =  "./results/europeC/final_metadata.tsv"
# args$n = 10
# demes = args$demes
# demes$exclude_country[5] = "France,Germany,Italy,Spain"
# demes <- demes %>% arrange(deme)
```

## Deme configuration
\tiny
```{r demeconfig}
# Load demes configuration and sequence metadata -------------------------------
demes <- data.frame(deme = NA, region = NA, country = NA, division = NA,
                    exclude_country = NA, exclude_division = NA,
                    min_date = NA, max_date = NA, seq_per_deme = NA) %>%
  bind_rows(bind_rows(lapply(yaml::yaml.load(string = gsub(",", ", ", gsub(":", ": ", args$demes))),
                          data.frame, stringsAsFactors = FALSE), .id = "deme")) %>%
  group_by(deme) %>%
  mutate(exclude_country = ifelse(is.na(exclude_country), NA, paste0(exclude_country, collapse = ","))) %>%
  distinct() %>%
  filter_all(any_vars(!is.na(.))) %>%
  mutate(deme = str_to_title(deme)) %>%
  mutate(deme = ifelse(deme %in% c("Othereuropean", "OtherEuropean"), "Other European", deme)) %>%
  arrange(deme)

@@

```{r first-bycountry, fig.height=4}
# 2.2b First introduction into each country, distribution density destination
m = 1
first_country <- df_traj %>%
  mutate(partner = ifelse(var == "O", "China", partner)) %>%
  # 1. Prepare data
  filter(var == "IM" & deme != "China"| var == "O" & deme == "China", !is.na(partner), value != 0) %>%
  group_by(traj, deme) %>%
  arrange(date, partner) %>%
  slice(1:m)

@@

```{r first-times, fig.height=4, include=FALSE}
# 2. First introduction distribution density by deme and time of first official reported case to ECDC
first_times <- df_traj_cases %>%
  # 1. Prepare data
  filter(var == "IM" | var == "O", value != 0) %>%
  group_by(deme, traj) %>%
  arrange(date) %>%
  slice(1) %>%
  ungroup %>%
  bind_rows(df_traj_cases %>%
              filter(var == "IM", value != 0) %>%
              group_by(traj) %>%
              arrange(date) %>%
              slice(1)  %>%
              mutate(deme = "Europe")) %>%
  mutate(deme = fct_rev(deme)) %>%
  # 2. Plot
  ggplot() +
  geom_density_ridges(aes(x = date, y = deme, fill = deme), color = "grey50", quantile_lines = TRUE, quantiles = c(0.025, 0.5, 0.975), bandwidth=2, alpha = 0.7, size = 0.2) +
  #stat_density_ridges(, alpha = 0.7)
  #geom_histogram(aes(x = date, fill = deme), bandwidth=5, alpha = 0.7, size = 0.2) +
  #geom_vline(aes(xintercept = min_date, color = dest), linetype = 2) +
  geom_point(data = first_ecdc, 
             aes(date, deme, fill = deme), color = "grey50", shape = 23, size = 3) +
  scale_fill_manual(values = c(dcolors, "Europe" = "grey")) +
  scale_color_manual(values = c(dcolors, "Europe" = "grey")) +
  scale_x_date(limits = c(ymd("2019-10-01"), ymd("2020-03-08")), date_breaks = "1 month", date_labels = "%b %Y", expand = c(0,0)) +
  scale_y_discrete(expand = c(0.05,0), "probability") +
  #theme_ridges() +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        panel.grid.major.x =  element_line(colour = "grey80", size = 0.3, linetype = 2),
        panel.grid.major.y =  element_line(colour = "grey80", size = 0.3, linetype = 1),
        #panel.grid.minor.x =  element_line(colour = "grey80", size = 0.2,  linetype = 3),
        #axis.title.y=element_blank(),
        panel.background = element_rect(fill = "white", colour = "white"))

@@

```{r bvsm-table, results = 'asis'}
for (d in demes$deme) {
  cat("\n## Local transmission vs imported cases - ", d, "\n")
  print(hsummary %>% filter(deme == d))
  cat("\n")
}
```

@@

:::: {.column width="50%"}

@@

## Weekly incidence population percentage
